Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-15 analysis/paper/paper.Rmd
remove open access policy figures

load(system.file("extdata",
                 "m_h1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_i1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
```

>>>>

load(system.file("extdata",
                 "m_h1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
```
